---
title: "Food For Thought"
author: "Rebecca Oh, Alexa Zmich"
date: "December 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: SURVMETH 727 Term Project
geometry: margin=0.75in
---

## Setup
```{r message=FALSE, warning=FALSE}
library(yelpr)
library(knitr)
library(markdown)
library(tidyverse)
library(httr)
library(RSocrata)
library(tidyverse)
library(stringr)
library(noncensus)
```

## Introduction

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Rising obesity rates in the United States have become a large concern, as obesity is now the leading preventable cause of death worldwide and is associated with many other causes of death. The dietary choices we make every day affect the potential of developing obesity, including the types of food establishments we choose to eat at. Thus, we are interested in seeing the possible effect these food establishments can have on our health, leading to our research question: “Is there a correlation between the main cuisines of food establishments and obesity rates within each Michigan county?”

## Methods (data (sources, gathering steps))

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In order to answer our main research question, we will first need Yelp API access. We have chosen Yelp as our data gathering source, as it stores information regarding restaurant name, cuisine type, and location, which we will later use to test for correlation against obesity. We will store Yelp's API key as an object, and we will use this object in the following API queries to ultimately form our dataset.

```{r}
#create a token for use with API request
client_id <- "tuUnFmtQQZAX7YHwwbdz6g"
client_secret <- "PQL5AXms_2Yr6szyGBy2V6yH1sdeFS1g5S3od1WZxFKAD3IK0DEHC0mt1B8atTzO5mspVGcqxvA9gbAb_3u3_u07umTpSr0_YTdcTH9B4sP1UEXrvn713CzqPhzTXXYx"

res <- POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
                        client_id = client_id,
                        client_secret = client_secret))

token <- content(res)$access_token
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In terms of data gathering, we are interested in collecting the top 20 most popular food establishments in the most populated location of each of the 83 counties (indicated in the commented code) in the state of Michigan. We will search with "food" as the term of interest and the "location" as the most populated area within the specific county.

```{r}
#search url and collect data per county
yelp <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #wayne
yelp2 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #oakland
yelp3 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #macomb
yelp4 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #kent
yelp5 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #genesee
yelp6 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ann+arbor+MI" #washtenaw
yelp7 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #ingham
yelp8 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #ottawa
yelp9 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #kalamazoo
yelp10 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #livingston
yelp11 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #saginaw
yelp12 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #muskegon
yelp13 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #st. clair
yelp14 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #jackson
yelp15 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #berrien
yelp16 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #monroe
yelp17 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #calhoun
yelp18 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #allegan
yelp19 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #eaton
yelp20 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #bay
yelp21 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #lenawee
yelp22 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #grand traverse
yelp23 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #lapeer
yelp24 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #midland
yelp25 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #clinton
yelp26 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #van buren
yelp27 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #isabella
yelp28 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #shiawassee
yelp29 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #marquette
yelp30 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #ionia
yelp31 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #montcalm
yelp32 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #barry
yelp33 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #st. joseph
yelp34 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #tuscola
yelp35 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #cass
yelp36 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #newaygo
yelp37 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #hillsdale
yelp38 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #branch
yelp39 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #mecosta
yelp40 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #sanilac
yelp41 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #gratiot
yelp42 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #chippewa
yelp43 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #houghton
yelp44 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #delta
yelp45 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #wexford
yelp46 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #emmet
yelp47 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #huron
yelp48 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #clare
yelp49 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #mason
yelp50 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #alpena
yelp51 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #oceana
yelp52 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #charlevoix
yelp53 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #cheboygan
yelp54 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #dickinson
yelp55 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #gladwin
yelp56 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #iosco
yelp57 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #otsego
yelp58 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #manistee
yelp59 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #roscommon
yelp60 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #antrim
yelp61 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #osceola
yelp62 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #menominee
yelp63 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #leelanau
yelp64 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #ogemaw
yelp65 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #kalkaska
yelp66 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #benzie
yelp67 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #missaukee
yelp68 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #gogebic
yelp69 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #arenac
yelp70 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #crawford
yelp71 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #presque isle
yelp72 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #lake
yelp73 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #iron
yelp74 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #mackinac
yelp75 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #alcona
yelp76 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #montmorency
yelp77 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #alger
yelp78 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #baraga
yelp79 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #oscoda
yelp80 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #schoolcraft
yelp81 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #luce
yelp82 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #ontonagon
yelp83 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=MI" #keweenaw

url <- modify_url(yelp, path = c("v3", "businesses", "search"))
url2 <- modify_url(yelp2, path = c("v3", "businesses", "search"))
url3 <- modify_url(yelp3, path = c("v3", "businesses", "search"))
url4 <- modify_url(yelp4, path = c("v3", "businesses", "search"))
url5 <- modify_url(yelp5, path = c("v3", "businesses", "search"))
url6 <- modify_url(yelp6, path = c("v3", "businesses", "search"))
url7 <- modify_url(yelp7, path = c("v3", "businesses", "search"))
url8 <- modify_url(yelp8, path = c("v3", "businesses", "search"))
url9 <- modify_url(yelp9, path = c("v3", "businesses", "search"))
url10 <- modify_url(yelp10, path = c("v3", "businesses", "search"))
url11 <- modify_url(yelp11, path = c("v3", "businesses", "search"))
url12 <- modify_url(yelp12, path = c("v3", "businesses", "search"))
url13 <- modify_url(yelp13, path = c("v3", "businesses", "search"))
url14 <- modify_url(yelp14, path = c("v3", "businesses", "search"))
url15 <- modify_url(yelp15, path = c("v3", "businesses", "search"))
url16 <- modify_url(yelp16, path = c("v3", "businesses", "search"))
url17 <- modify_url(yelp17, path = c("v3", "businesses", "search"))
url18 <- modify_url(yelp18, path = c("v3", "businesses", "search"))
url19 <- modify_url(yelp19, path = c("v3", "businesses", "search"))
url20 <- modify_url(yelp20, path = c("v3", "businesses", "search"))
url21 <- modify_url(yelp21, path = c("v3", "businesses", "search"))
url22 <- modify_url(yelp22, path = c("v3", "businesses", "search"))
url23 <- modify_url(yelp23, path = c("v3", "businesses", "search"))
url24 <- modify_url(yelp24, path = c("v3", "businesses", "search"))
url25 <- modify_url(yelp25, path = c("v3", "businesses", "search"))
url26 <- modify_url(yelp26, path = c("v3", "businesses", "search"))
url27 <- modify_url(yelp27, path = c("v3", "businesses", "search"))
url28 <- modify_url(yelp28, path = c("v3", "businesses", "search"))
url29 <- modify_url(yelp29, path = c("v3", "businesses", "search"))
url30 <- modify_url(yelp30, path = c("v3", "businesses", "search"))
url31 <- modify_url(yelp31, path = c("v3", "businesses", "search"))
url32 <- modify_url(yelp32, path = c("v3", "businesses", "search"))
url33 <- modify_url(yelp33, path = c("v3", "businesses", "search"))
url34 <- modify_url(yelp34, path = c("v3", "businesses", "search"))
url35 <- modify_url(yelp35, path = c("v3", "businesses", "search"))
url36 <- modify_url(yelp36, path = c("v3", "businesses", "search"))
url37 <- modify_url(yelp37, path = c("v3", "businesses", "search"))
url38 <- modify_url(yelp38, path = c("v3", "businesses", "search"))
url39 <- modify_url(yelp39, path = c("v3", "businesses", "search"))
url40 <- modify_url(yelp40, path = c("v3", "businesses", "search"))
url41 <- modify_url(yelp41, path = c("v3", "businesses", "search"))
url42 <- modify_url(yelp42, path = c("v3", "businesses", "search"))
url43 <- modify_url(yelp43, path = c("v3", "businesses", "search"))
url44 <- modify_url(yelp44, path = c("v3", "businesses", "search"))
url45 <- modify_url(yelp45, path = c("v3", "businesses", "search"))
url46 <- modify_url(yelp46, path = c("v3", "businesses", "search"))
url47 <- modify_url(yelp47, path = c("v3", "businesses", "search"))
url48 <- modify_url(yelp48, path = c("v3", "businesses", "search"))
url49 <- modify_url(yelp49, path = c("v3", "businesses", "search"))
url50 <- modify_url(yelp50, path = c("v3", "businesses", "search"))
url51 <- modify_url(yelp51, path = c("v3", "businesses", "search"))
url52 <- modify_url(yelp52, path = c("v3", "businesses", "search"))
url53 <- modify_url(yelp53, path = c("v3", "businesses", "search"))
url54 <- modify_url(yelp54, path = c("v3", "businesses", "search"))
url55 <- modify_url(yelp55, path = c("v3", "businesses", "search"))
url56 <- modify_url(yelp56, path = c("v3", "businesses", "search"))
url57 <- modify_url(yelp57, path = c("v3", "businesses", "search"))
url58 <- modify_url(yelp58, path = c("v3", "businesses", "search"))
url59 <- modify_url(yelp59, path = c("v3", "businesses", "search"))
url60 <- modify_url(yelp60, path = c("v3", "businesses", "search"))
url61 <- modify_url(yelp61, path = c("v3", "businesses", "search"))
url62 <- modify_url(yelp62, path = c("v3", "businesses", "search"))
url63 <- modify_url(yelp63, path = c("v3", "businesses", "search"))
url64 <- modify_url(yelp64, path = c("v3", "businesses", "search"))
url65 <- modify_url(yelp65, path = c("v3", "businesses", "search"))
url66 <- modify_url(yelp66, path = c("v3", "businesses", "search"))
url67 <- modify_url(yelp67, path = c("v3", "businesses", "search"))
url68 <- modify_url(yelp68, path = c("v3", "businesses", "search"))
url69 <- modify_url(yelp69, path = c("v3", "businesses", "search"))
url70 <- modify_url(yelp70, path = c("v3", "businesses", "search"))
url71 <- modify_url(yelp71, path = c("v3", "businesses", "search"))
url72 <- modify_url(yelp72, path = c("v3", "businesses", "search"))
url73 <- modify_url(yelp73, path = c("v3", "businesses", "search"))
url74 <- modify_url(yelp74, path = c("v3", "businesses", "search"))
url75 <- modify_url(yelp75, path = c("v3", "businesses", "search"))
url76 <- modify_url(yelp76, path = c("v3", "businesses", "search"))
url77 <- modify_url(yelp77, path = c("v3", "businesses", "search"))
url78 <- modify_url(yelp78, path = c("v3", "businesses", "search"))
url79 <- modify_url(yelp79, path = c("v3", "businesses", "search"))
url80 <- modify_url(yelp80, path = c("v3", "businesses", "search"))
url81 <- modify_url(yelp81, path = c("v3", "businesses", "search"))
url82 <- modify_url(yelp82, path = c("v3", "businesses", "search"))
url83 <- modify_url(yelp83, path = c("v3", "businesses", "search"))

res <- GET(url, add_headers('Authorization' = paste("bearer", client_secret)))
res2 <- GET(url2, add_headers('Authorization' = paste("bearer", client_secret)))
res3 <- GET(url3, add_headers('Authorization' = paste("bearer", client_secret)))
res4 <- GET(url4, add_headers('Authorization' = paste("bearer", client_secret)))
res5 <- GET(url5, add_headers('Authorization' = paste("bearer", client_secret)))
res6 <- GET(url6, add_headers('Authorization' = paste("bearer", client_secret)))
res7 <- GET(url7, add_headers('Authorization' = paste("bearer", client_secret)))
res8 <- GET(url8, add_headers('Authorization' = paste("bearer", client_secret)))
res9 <- GET(url9, add_headers('Authorization' = paste("bearer", client_secret)))
res10 <- GET(url10, add_headers('Authorization' = paste("bearer", client_secret)))
res11 <- GET(url11, add_headers('Authorization' = paste("bearer", client_secret)))
res12 <- GET(url12, add_headers('Authorization' = paste("bearer", client_secret)))
res13 <- GET(url13, add_headers('Authorization' = paste("bearer", client_secret)))
res14 <- GET(url14, add_headers('Authorization' = paste("bearer", client_secret)))
res15 <- GET(url15, add_headers('Authorization' = paste("bearer", client_secret)))
res16 <- GET(url16, add_headers('Authorization' = paste("bearer", client_secret)))
res17 <- GET(url17, add_headers('Authorization' = paste("bearer", client_secret)))
res18 <- GET(url18, add_headers('Authorization' = paste("bearer", client_secret)))
res19 <- GET(url19, add_headers('Authorization' = paste("bearer", client_secret)))
res20 <- GET(url20, add_headers('Authorization' = paste("bearer", client_secret)))
res21 <- GET(url21, add_headers('Authorization' = paste("bearer", client_secret)))
res22 <- GET(url22, add_headers('Authorization' = paste("bearer", client_secret)))
res23 <- GET(url23, add_headers('Authorization' = paste("bearer", client_secret)))
res24 <- GET(url24, add_headers('Authorization' = paste("bearer", client_secret)))
res25 <- GET(url25, add_headers('Authorization' = paste("bearer", client_secret)))
res26 <- GET(url26, add_headers('Authorization' = paste("bearer", client_secret)))
res27 <- GET(url27, add_headers('Authorization' = paste("bearer", client_secret)))
res28 <- GET(url28, add_headers('Authorization' = paste("bearer", client_secret)))
res29 <- GET(url29, add_headers('Authorization' = paste("bearer", client_secret)))
res30 <- GET(url30, add_headers('Authorization' = paste("bearer", client_secret)))
res31 <- GET(url31, add_headers('Authorization' = paste("bearer", client_secret)))
res32 <- GET(url32, add_headers('Authorization' = paste("bearer", client_secret)))
res33 <- GET(url33, add_headers('Authorization' = paste("bearer", client_secret)))
res34 <- GET(url34, add_headers('Authorization' = paste("bearer", client_secret)))
res35 <- GET(url35, add_headers('Authorization' = paste("bearer", client_secret)))
res36 <- GET(url36, add_headers('Authorization' = paste("bearer", client_secret)))
res37 <- GET(url37, add_headers('Authorization' = paste("bearer", client_secret)))
res38 <- GET(url38, add_headers('Authorization' = paste("bearer", client_secret)))
res39 <- GET(url39, add_headers('Authorization' = paste("bearer", client_secret)))
res40 <- GET(url40, add_headers('Authorization' = paste("bearer", client_secret)))
res41 <- GET(url41, add_headers('Authorization' = paste("bearer", client_secret)))
res42 <- GET(url42, add_headers('Authorization' = paste("bearer", client_secret)))
res43 <- GET(url43, add_headers('Authorization' = paste("bearer", client_secret)))
res44 <- GET(url44, add_headers('Authorization' = paste("bearer", client_secret)))
res45 <- GET(url45, add_headers('Authorization' = paste("bearer", client_secret)))
res46 <- GET(url46, add_headers('Authorization' = paste("bearer", client_secret)))
res47 <- GET(url47, add_headers('Authorization' = paste("bearer", client_secret)))
res48 <- GET(url48, add_headers('Authorization' = paste("bearer", client_secret)))
res49 <- GET(url49, add_headers('Authorization' = paste("bearer", client_secret)))
res50 <- GET(url50, add_headers('Authorization' = paste("bearer", client_secret)))
res51 <- GET(url51, add_headers('Authorization' = paste("bearer", client_secret)))
res52 <- GET(url52, add_headers('Authorization' = paste("bearer", client_secret)))
res53 <- GET(url53, add_headers('Authorization' = paste("bearer", client_secret)))
res54 <- GET(url54, add_headers('Authorization' = paste("bearer", client_secret)))
res55 <- GET(url55, add_headers('Authorization' = paste("bearer", client_secret)))
res56 <- GET(url56, add_headers('Authorization' = paste("bearer", client_secret)))
res57 <- GET(url57, add_headers('Authorization' = paste("bearer", client_secret)))
res58 <- GET(url58, add_headers('Authorization' = paste("bearer", client_secret)))
res59 <- GET(url59, add_headers('Authorization' = paste("bearer", client_secret)))
res60 <- GET(url60, add_headers('Authorization' = paste("bearer", client_secret)))
res61 <- GET(url61, add_headers('Authorization' = paste("bearer", client_secret)))
res62 <- GET(url62, add_headers('Authorization' = paste("bearer", client_secret)))
res63 <- GET(url63, add_headers('Authorization' = paste("bearer", client_secret)))
res64 <- GET(url64, add_headers('Authorization' = paste("bearer", client_secret)))
res65 <- GET(url65, add_headers('Authorization' = paste("bearer", client_secret)))
res66 <- GET(url66, add_headers('Authorization' = paste("bearer", client_secret)))
res67 <- GET(url67, add_headers('Authorization' = paste("bearer", client_secret)))
res68 <- GET(url68, add_headers('Authorization' = paste("bearer", client_secret)))
res69 <- GET(url69, add_headers('Authorization' = paste("bearer", client_secret)))
res70 <- GET(url70, add_headers('Authorization' = paste("bearer", client_secret)))
res71 <- GET(url71, add_headers('Authorization' = paste("bearer", client_secret)))
res72 <- GET(url72, add_headers('Authorization' = paste("bearer", client_secret)))
res73 <- GET(url73, add_headers('Authorization' = paste("bearer", client_secret)))
res74 <- GET(url74, add_headers('Authorization' = paste("bearer", client_secret)))
res75 <- GET(url75, add_headers('Authorization' = paste("bearer", client_secret)))
res76 <- GET(url76, add_headers('Authorization' = paste("bearer", client_secret)))
res77 <- GET(url77, add_headers('Authorization' = paste("bearer", client_secret)))
res78 <- GET(url78, add_headers('Authorization' = paste("bearer", client_secret)))
res79 <- GET(url79, add_headers('Authorization' = paste("bearer", client_secret)))
res80 <- GET(url80, add_headers('Authorization' = paste("bearer", client_secret)))
res81 <- GET(url81, add_headers('Authorization' = paste("bearer", client_secret)))
res82 <- GET(url82, add_headers('Authorization' = paste("bearer", client_secret)))
res83 <- GET(url83, add_headers('Authorization' = paste("bearer", client_secret)))

results <- content(res)
results2 <- content(res2)
results3 <- content(res3)
results4 <- content(res4)
results5 <- content(res5)
results6 <- content(res6)
results7 <- content(res7)
results8 <- content(res8)
results9 <- content(res9)
results10 <- content(res10)
results11 <- content(res11)
results12 <- content(res12)
results13 <- content(res13)
results14 <- content(res14)
results15 <- content(res15)
results16 <- content(res16)
results17 <- content(res17)
results18 <- content(res18)
results19 <- content(res19)
results20 <- content(res20)
results21 <- content(res21)
results22 <- content(res22)
results23 <- content(res23)
results24 <- content(res24)
results25 <- content(res25)
results26 <- content(res26)
results27 <- content(res27)
results28 <- content(res28)
results29 <- content(res29)
results30 <- content(res30)
results31 <- content(res31)
results32 <- content(res32)
results33 <- content(res33)
results34 <- content(res34)
results35 <- content(res35)
results36 <- content(res36)
results37 <- content(res37)
results38 <- content(res38)
results39 <- content(res39)
results40 <- content(res40)
results41 <- content(res41)
results42 <- content(res42)
results43 <- content(res43)
results44 <- content(res44)
results45 <- content(res45)
results46 <- content(res46)
results47 <- content(res47)
results48 <- content(res48)
results49 <- content(res49)
results50 <- content(res50)
results51 <- content(res51)
results52 <- content(res52)
results53 <- content(res53)
results54 <- content(res54)
results55 <- content(res55)
results56 <- content(res56)
results57 <- content(res57)
results58 <- content(res58)
results59 <- content(res59)
results60 <- content(res60)
results61 <- content(res61)
results62 <- content(res62)
results63 <- content(res63)
results64 <- content(res64)
results65 <- content(res65)
results66 <- content(res66)
results67 <- content(res67)
results68 <- content(res68)
results69 <- content(res69)
results70 <- content(res70)
results71 <- content(res71)
results72 <- content(res72)
results73 <- content(res73)
results74 <- content(res74)
results75 <- content(res75)
results76 <- content(res76)
results77 <- content(res77)
results78 <- content(res78)
results79 <- content(res79)
results80 <- content(res80)
results81 <- content(res81)
results82 <- content(res82)
results83 <- content(res83)

#parse data
yelp_httr_parse <- function(x) {

  parse_list <- list(id = x$id, 
                     name = x$name, 
                     categories = x$categories, 
                     rating = x$rating, 
                     review_count = x$review_count, 
                     latitude = x$coordinates$latitude, 
                     longitude = x$coordinates$longitude, 
                     address1 = x$location$address1, 
                     city = x$location$city, 
                     state = x$location$state, 
                     distance = x$distance)
  
  parse_list <- lapply(parse_list, FUN = function(x) ifelse(is.null(x), "", x))
  
  df <- tibble(id=parse_list$id,
                   name=parse_list$name, 
                   categories = parse_list$categories, 
                   rating = parse_list$rating, 
                   review_count = parse_list$review_count, 
                   latitude=parse_list$latitude, 
                   longitude = parse_list$longitude, 
                   address1 = parse_list$address1, 
                   city = parse_list$city, 
                   state = parse_list$state, 
                   distance= parse_list$distance)
  df
}

results_list <- lapply(results$businesses, FUN = yelp_httr_parse)
results_list2 <- lapply(results2$businesses, FUN = yelp_httr_parse)
results_list3 <- lapply(results3$businesses, FUN = yelp_httr_parse)
results_list4 <- lapply(results4$businesses, FUN = yelp_httr_parse)
results_list5 <- lapply(results5$businesses, FUN = yelp_httr_parse)
results_list6 <- lapply(results6$businesses, FUN = yelp_httr_parse)
results_list7 <- lapply(results7$businesses, FUN = yelp_httr_parse)
results_list8 <- lapply(results8$businesses, FUN = yelp_httr_parse)
results_list9 <- lapply(results9$businesses, FUN = yelp_httr_parse)
results_list10 <- lapply(results10$businesses, FUN = yelp_httr_parse)
results_list11 <- lapply(results11$businesses, FUN = yelp_httr_parse)
results_list12 <- lapply(results12$businesses, FUN = yelp_httr_parse)
results_list13 <- lapply(results13$businesses, FUN = yelp_httr_parse)
results_list14 <- lapply(results14$businesses, FUN = yelp_httr_parse)
results_list15 <- lapply(results15$businesses, FUN = yelp_httr_parse)
results_list16 <- lapply(results16$businesses, FUN = yelp_httr_parse)
results_list17 <- lapply(results17$businesses, FUN = yelp_httr_parse)
results_list18 <- lapply(results18$businesses, FUN = yelp_httr_parse)
results_list19 <- lapply(results19$businesses, FUN = yelp_httr_parse)
results_list20 <- lapply(results20$businesses, FUN = yelp_httr_parse)
results_list21 <- lapply(results21$businesses, FUN = yelp_httr_parse)
results_list22 <- lapply(results22$businesses, FUN = yelp_httr_parse)
results_list23 <- lapply(results23$businesses, FUN = yelp_httr_parse)
results_list24 <- lapply(results24$businesses, FUN = yelp_httr_parse)
results_list25 <- lapply(results25$businesses, FUN = yelp_httr_parse)
results_list26 <- lapply(results26$businesses, FUN = yelp_httr_parse)
results_list27 <- lapply(results27$businesses, FUN = yelp_httr_parse)
results_list28 <- lapply(results28$businesses, FUN = yelp_httr_parse)
results_list29 <- lapply(results29$businesses, FUN = yelp_httr_parse)
results_list30 <- lapply(results30$businesses, FUN = yelp_httr_parse)
results_list31 <- lapply(results31$businesses, FUN = yelp_httr_parse)
results_list32 <- lapply(results32$businesses, FUN = yelp_httr_parse)
results_list33 <- lapply(results33$businesses, FUN = yelp_httr_parse)
results_list34 <- lapply(results34$businesses, FUN = yelp_httr_parse)
results_list35 <- lapply(results35$businesses, FUN = yelp_httr_parse)
results_list36 <- lapply(results36$businesses, FUN = yelp_httr_parse)
results_list37 <- lapply(results37$businesses, FUN = yelp_httr_parse)
results_list38 <- lapply(results38$businesses, FUN = yelp_httr_parse)
results_list39 <- lapply(results39$businesses, FUN = yelp_httr_parse)
results_list40 <- lapply(results40$businesses, FUN = yelp_httr_parse)
results_list41 <- lapply(results41$businesses, FUN = yelp_httr_parse)
results_list42 <- lapply(results42$businesses, FUN = yelp_httr_parse)
results_list43 <- lapply(results43$businesses, FUN = yelp_httr_parse)
results_list44 <- lapply(results44$businesses, FUN = yelp_httr_parse)
results_list45 <- lapply(results45$businesses, FUN = yelp_httr_parse)
results_list46 <- lapply(results46$businesses, FUN = yelp_httr_parse)
results_list47 <- lapply(results47$businesses, FUN = yelp_httr_parse)
results_list48 <- lapply(results48$businesses, FUN = yelp_httr_parse)
results_list49 <- lapply(results49$businesses, FUN = yelp_httr_parse)
results_list50 <- lapply(results50$businesses, FUN = yelp_httr_parse)
results_list51 <- lapply(results51$businesses, FUN = yelp_httr_parse)
results_list52 <- lapply(results52$businesses, FUN = yelp_httr_parse)
results_list53 <- lapply(results53$businesses, FUN = yelp_httr_parse)
results_list54 <- lapply(results54$businesses, FUN = yelp_httr_parse)
results_list55 <- lapply(results55$businesses, FUN = yelp_httr_parse)
results_list56 <- lapply(results56$businesses, FUN = yelp_httr_parse)
results_list57 <- lapply(results57$businesses, FUN = yelp_httr_parse)
results_list58 <- lapply(results58$businesses, FUN = yelp_httr_parse)
results_list59 <- lapply(results59$businesses, FUN = yelp_httr_parse)
results_list60 <- lapply(results60$businesses, FUN = yelp_httr_parse)
results_list61 <- lapply(results61$businesses, FUN = yelp_httr_parse)
results_list62 <- lapply(results62$businesses, FUN = yelp_httr_parse)
results_list63 <- lapply(results63$businesses, FUN = yelp_httr_parse)
results_list64 <- lapply(results64$businesses, FUN = yelp_httr_parse)
results_list65 <- lapply(results65$businesses, FUN = yelp_httr_parse)
results_list66 <- lapply(results66$businesses, FUN = yelp_httr_parse)
results_list67 <- lapply(results67$businesses, FUN = yelp_httr_parse)
results_list68 <- lapply(results68$businesses, FUN = yelp_httr_parse)
results_list69 <- lapply(results69$businesses, FUN = yelp_httr_parse)
results_list70 <- lapply(results70$businesses, FUN = yelp_httr_parse)
results_list71 <- lapply(results71$businesses, FUN = yelp_httr_parse)
results_list72 <- lapply(results72$businesses, FUN = yelp_httr_parse)
results_list73 <- lapply(results73$businesses, FUN = yelp_httr_parse)
results_list74 <- lapply(results74$businesses, FUN = yelp_httr_parse)
results_list75 <- lapply(results75$businesses, FUN = yelp_httr_parse)
results_list76 <- lapply(results76$businesses, FUN = yelp_httr_parse)
results_list77 <- lapply(results77$businesses, FUN = yelp_httr_parse)
results_list78 <- lapply(results78$businesses, FUN = yelp_httr_parse)
results_list79 <- lapply(results79$businesses, FUN = yelp_httr_parse)
results_list80 <- lapply(results80$businesses, FUN = yelp_httr_parse)
results_list81 <- lapply(results81$businesses, FUN = yelp_httr_parse)
results_list82 <- lapply(results82$businesses, FUN = yelp_httr_parse)
results_list83 <- lapply(results83$businesses, FUN = yelp_httr_parse)

food_data <- do.call("rbind", results_list)
food_data2 <- do.call("rbind", results_list2)
food_data3 <- do.call("rbind", results_list3)
food_data4 <- do.call("rbind", results_list4)
food_data5 <- do.call("rbind", results_list5)
food_data6 <- do.call("rbind", results_list6)
food_data7 <- do.call("rbind", results_list7)
food_data8 <- do.call("rbind", results_list8)
food_data9 <- do.call("rbind", results_list9)
food_data10 <- do.call("rbind", results_list10)
food_data11 <- do.call("rbind", results_list11)
food_data12 <- do.call("rbind", results_list12)
food_data13 <- do.call("rbind", results_list13)
food_data14 <- do.call("rbind", results_list14)
food_data15 <- do.call("rbind", results_list15)
food_data16 <- do.call("rbind", results_list16)
food_data17 <- do.call("rbind", results_list17)
food_data18 <- do.call("rbind", results_list18)
food_data19 <- do.call("rbind", results_list19)
food_data20 <- do.call("rbind", results_list20)
food_data21 <- do.call("rbind", results_list21)
food_data22 <- do.call("rbind", results_list22)
food_data23 <- do.call("rbind", results_list23)
food_data24 <- do.call("rbind", results_list24)
food_data25 <- do.call("rbind", results_list25)
food_data26 <- do.call("rbind", results_list26)
food_data27 <- do.call("rbind", results_list27)
food_data28 <- do.call("rbind", results_list28)
food_data29 <- do.call("rbind", results_list29)
food_data30 <- do.call("rbind", results_list30)
food_data31 <- do.call("rbind", results_list31)
food_data32 <- do.call("rbind", results_list32)
food_data33 <- do.call("rbind", results_list33)
food_data34 <- do.call("rbind", results_list34)
food_data35 <- do.call("rbind", results_list35)
food_data36 <- do.call("rbind", results_list36)
food_data37 <- do.call("rbind", results_list37)
food_data38 <- do.call("rbind", results_list38)
food_data39 <- do.call("rbind", results_list39)
food_data40 <- do.call("rbind", results_list40)
food_data41 <- do.call("rbind", results_list41)
food_data42 <- do.call("rbind", results_list42)
food_data43 <- do.call("rbind", results_list43)
food_data44 <- do.call("rbind", results_list44)
food_data45 <- do.call("rbind", results_list45)
food_data46 <- do.call("rbind", results_list46)
food_data47 <- do.call("rbind", results_list47)
food_data48 <- do.call("rbind", results_list48)
food_data49 <- do.call("rbind", results_list49)
food_data50 <- do.call("rbind", results_list50)
food_data51 <- do.call("rbind", results_list51)
food_data52 <- do.call("rbind", results_list52)
food_data53 <- do.call("rbind", results_list53)
food_data54 <- do.call("rbind", results_list54)
food_data55 <- do.call("rbind", results_list55)
food_data56 <- do.call("rbind", results_list56)
food_data57 <- do.call("rbind", results_list57)
food_data58 <- do.call("rbind", results_list58)
food_data59 <- do.call("rbind", results_list59)
food_data60 <- do.call("rbind", results_list60)
food_data61 <- do.call("rbind", results_list61)
food_data62 <- do.call("rbind", results_list62)
food_data63 <- do.call("rbind", results_list63)
food_data64 <- do.call("rbind", results_list64)
food_data65 <- do.call("rbind", results_list65)
food_data66 <- do.call("rbind", results_list66)
food_data67 <- do.call("rbind", results_list67)
food_data68 <- do.call("rbind", results_list68)
food_data69 <- do.call("rbind", results_list69)
food_data70 <- do.call("rbind", results_list70)
food_data71 <- do.call("rbind", results_list71)
food_data72 <- do.call("rbind", results_list72)
food_data73 <- do.call("rbind", results_list73)
food_data74 <- do.call("rbind", results_list74)
food_data75 <- do.call("rbind", results_list75)
food_data76 <- do.call("rbind", results_list76)
food_data77 <- do.call("rbind", results_list77)
food_data78 <- do.call("rbind", results_list78)
food_data79 <- do.call("rbind", results_list79)
food_data80 <- do.call("rbind", results_list80)
food_data81 <- do.call("rbind", results_list81)
food_data82 <- do.call("rbind", results_list82)
food_data83 <- do.call("rbind", results_list83)

all_establishments <- rbind(
  food_data, 
  food_data2, 
  food_data3,
  food_data4,
  food_data5,
  food_data6,
  food_data7,
  food_data8,
  food_data9, 
  food_data10,
  food_data11,
  food_data12,
  food_data13,
  food_data14,
  food_data15,
  food_data16,
  food_data17,
  food_data18,
  food_data19,
  food_data20,
  food_data21,
  food_data22,
  food_data23,
  food_data24,
  food_data25,
  food_data26,
  food_data27,
  food_data28,
  food_data29,
  food_data30,
  food_data31,
  food_data32,
  food_data33,
  food_data34,
  food_data35,
  food_data36,
  food_data37,
  food_data38,
  food_data39,
  food_data40,
  food_data41,
  food_data42,
  food_data43,
  food_data44,
  food_data45,
  food_data46,
  food_data47,
  food_data48,
  food_data49,
  food_data50,
  food_data51,
  food_data52,
  food_data53,
  food_data54,
  food_data55,
  food_data56,
  food_data57,
  food_data58,
  food_data59,
  food_data60,
  food_data61,
  food_data62,
  food_data63,
  food_data64,
  food_data65,
  food_data66,
  food_data67,
  food_data68,
  food_data69,
  food_data70,
  food_data71,
  food_data72,
  food_data73,
  food_data74,
  food_data75,
  food_data76,
  food_data77,
  food_data78,
  food_data79,
  food_data80,
  food_data81,
  food_data82,
  food_data83)
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;One of the columns of interest in our dataset (all_establishments), 'categories', requires some clean-up with formatting. Thus, we will reformat that column in order to make it more understandable and clear.

```{r results='hide', message=FALSE, warning=FALSE}
#clean up data
all_establishments$categories <- all_establishments$categories %>%
  str_replace_all(., "list\\(alias = ", "") %>%
  str_replace_all(., "\\)", "") %>%
  str_replace_all(., "\\(New", "- New") %>%
  str_replace_all(., "\\(Traditional", "- Traditional") %>%
  str_replace_all(., "newamerican", "") %>%
  str_replace_all(., ", title = ", "") %>%
  str_replace_all(., "\"", "") %>%
  str_replace_all(., "burgers", "") %>%
  str_replace_all(., "beergardens", "") %>%
  str_replace_all(., "bars", "") %>%
  str_replace_all(., "mediterranean", "") %>%
  str_replace_all(., "noodles", "") %>%
  str_replace_all(., "breakfast_brunch", "") %>%
  str_replace_all(., "himalayan", "") %>%
  str_replace_all(., "thai", "") %>%
  str_replace_all(., "restaurants", "") %>%
  str_replace_all(., "mexican", "") %>%
  str_replace_all(., "pizza", "") %>%
  str_replace_all(., "ramen", "") %>%
  str_replace_all(., "tacos", "") %>%
  str_replace_all(., "gastropubs", "") %>%
  str_replace_all(., "asianfusion", "") %>%
  str_replace_all(., "comfortfood", "") %>%
  str_replace_all(., "tradamerican", "") %>%
  str_replace_all(., "sports", "") %>%
  str_replace_all(., "french", "") %>%
  str_replace_all(., "foodtrucks", "") %>%
  str_replace_all(., "african", "") %>%
  str_replace_all(., "pubs", "") %>%
  str_replace_all(., "cuban", "") %>%
  str_replace_all(., "hotdog", "") %>%
  str_replace_all(., "diners", "") %>%
  str_replace_all(., "delis", "") %>%
  str_replace_all(., "caribbean", "") %>%
  str_replace_all(., "musicvenues", "") %>%
  str_replace_all(., "soulfood", "") %>%
  str_replace_all(., "chickenshop", "") %>%
  str_replace_all(., "bagels", "") %>%
  str_replace_all(., "italian", "") %>%
  str_replace_all(., "vietnamese", "") %>%
  str_replace_all(., "sandwiches", "") %>%
  str_replace_all(., "honduran", "") %>%
  str_replace_all(., "lebanese", "") %>%
  str_replace_all(., "bbq", "") %>%
  str_replace_all(., "chicken_wings", "") %>%
  str_replace_all(., "modern_european", "") %>%
  str_replace_all(., "chinese", "") %>%
  str_replace_all(., "breweries", "") %>%
  str_replace_all(., "vegan", "") %>%
  str_replace_all(., "salvadoran", "") %>%
  str_replace_all(., "venezuelan", "") %>%
  str_replace_all(., "sushi", "") %>%
  str_replace_all(., "filipino", "") %>%
  str_replace_all(., "icecream", "") %>%
  str_replace_all(., "halal", "") %>%
  str_replace_all(., "juice", "") %>%
  str_replace_all(., "sFast Food", "Fast Food") %>%
  str_replace_all(., "bakeries", "") %>%
  str_replace_all(., "poutineries", "") %>%
  str_replace_all(., "newcanadian", "") %>%
  str_replace_all(., "cocktail", "") %>%
  str_replace_all(., "brazilian", "") %>%
  str_replace_all(., "seafood", "") %>%
  str_replace_all(., "mideastern", "") %>%
  str_replace_all(., "polish", "") %>%
  str_replace_all(., "creperies", "") %>%
  str_replace_all(., "coffee", "") %>%
  str_replace_all(., "smokehouse", "") %>%
  str_replace_all(., "grocery", "") %>%
  str_replace_all(., "peruvian", "") %>%
  str_replace_all(., "tapas", "") %>%
  str_replace_all(., "senegalese", "") %>%
  str_replace_all(., "dive", "") %>%
  str_replace_all(., "dominican", "") %>%
  str_replace_all(., "fishnchips", "") %>%
  str_replace_all(., "japanese", "") %>%
  str_replace_all(., "german", "") %>%
  str_replace_all(., "food_court", "") %>%
  str_replace_all(., "cafes", "") %>%
  str_replace_all(., "puertorican", "") %>%
  str_replace_all(., "dimsum", "") %>%
  str_replace_all(., "meats", "") %>%
  str_replace_all(., "greek", "") %>%
  str_replace_all(., "fooddeliveryservices", "") %>%
  str_replace_all(., "moroccan", "") %>%
  str_replace_all(., "vegetarian", "") %>%
  str_replace_all(., "gourmet", "") %>%
  str_replace_all(., "streetvendors", "") %>%
  str_replace_all(., "salad", "") %>%
  str_replace_all(., "indpak", "") %>%
  str_replace_all(., "desserts", "") %>%
  str_replace_all(., "steak", "") %>%
  str_replace_all(., "seafoodmarkets", "") %>%
  str_replace_all(., "latin", "") %>%
  str_replace_all(., "tapasmallplates", "") %>%
  str_replace_all(., "mallplates", "") %>%
  str_replace_all(., "farmersmarket", "") %>%
  str_replace_all(., "british", "") %>%
  str_replace_all(., "korean", "") %>%
  str_replace_all(., "ukrainian", "") %>%
  str_replace_all(., "beer_and_wine", "") %>%
  str_replace_all(., "massage_therapy", "") %>%
  str_replace_all(., "cheeses", "") %>%
  str_replace_all(., "diyfood", "") %>%
  str_replace_all(., "soup", "") %>%
  str_replace_all(., "cajun", "") %>%
  str_replace_all(., "nightlife", "") %>%
  str_replace_all(., "cakeshop", "") %>%
  str_replace_all(., "ethiopian", "") %>%
  str_replace_all(., "customcakes", "") %>%
  str_replace_all(., "southern", "") %>%
  str_replace_all(., "foodstands", "") %>%
  str_replace_all(., "wine_", "") %>%
  str_replace_all(., "kebab", "") %>%
  str_replace_all(., "distilleries", "") %>%
  str_replace_all(., "dinnertheater", "") %>%
  str_replace_all(., "poke", "") %>%
  str_replace_all(., "teaTea", "Tea") %>%
  str_replace_all(., "social_clubs", "") %>%
  str_replace_all(., "markets", "") %>%
  str_replace_all(., "popcorn", "") %>%
  str_replace_all(., "buffets", "") %>%
  str_replace_all(., "importedfood", "")
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;The data from Yelp provides us information regarding location (city, state, longtitude, latitude). However, we are interested in studying counties within the state of Michigan. Thus, we will create an object that will map the restaurant's location to its associated county.
```{r}

```


## Results (e.g.  graphs, exploratory analysis)

## References