---
title: "Food For Thought"
author: "Rebecca Oh, Alexa Zmich"
date: "November 25, 2019"
output:
  pdf_document: 
    toc: yes
subtitle: SURVMETH 727 Term Project
geometry: margin=0.75in
references:
- id: Wickham2014
  title: Tidy Data
  author:
  - family: Wickham
    given: Hadley
  container-title: Journal of Statistical Software
  volume: 59
  issue: 10
  page: 1-23
  type: article-journal
  issued:
    year: 2014
- id: Baumer2017
  title: Modern Data Science with R
  author:
  - family: Baumer
    given: Benjamin S.
  - family: Kaplan
    given: Daniel T.
  - family: Horton
    given: Nicholas J.
  type: book
  publisher: Chapman \& Hall/CRC Press.
  issued:
    year: 2017
---

```{r, include = FALSE}
library(RSocrata)
library(ggmap)
library(yelpr)
library(knitr)
library(markdown)
library(tidyverse)
library(httr)
library(RSocrata)
library(tidyverse)
library(stringr)
library(noncensus)
library(readr)
library(dplyr)
library(lubridate)
library(corrplot)
library(magrittr)
library(factoextra)
library(cluster)
library(censusapi)
library(ggplot2)
library(Hmisc)
library(gridExtra)
```

## Introduction

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;(note from Christoph: This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Rising obesity rates in the United States have become a large concern, as obesity is now the leading preventable cause of death worldwide and is associated with many other causes of death. The dietary choices we make every day affect the potential of developing obesity, including the types of food establishments we choose to eat at. Thus, we are interested in seeing the possible effect these food establishments can have on our health, leading to our research question: “Is there a correlation between the main cuisines of food establishments and obesity rates within each Michigan county?”

## Data

### _Cuisines and Counties Data_

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In order to answer our main research question, we will first need to gather data regarding main cuisines in Michigan counties. We will will need Yelp API access. We have chosen Yelp as our data gathering source, as it stores information regarding restaurant name, cuisine type, and location, which we will later use to test for correlation against obesity. We will store Yelp's API key as an object, and we will use this object in the following API queries to ultimately form our dataset.

```{r}
#create a token for use with API request
client_id <- "tuUnFmtQQZAX7YHwwbdz6g"
client_secret <- "PQL5AXms_2Yr6szyGBy2V6yH1sdeFS1g5S3od1WZxFKAD3IK0DEHC0mt1B8atTzO5mspVGcqxvA9gbAb_3u3_u07umTpSr0_YTdcTH9B4sP1UEXrvn713CzqPhzTXXYx"

res <- POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
                        client_id = client_id,
                        client_secret = client_secret))

token <- content(res)$access_token
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In terms of data gathering, the Yelp API does not support gathering data by searching a whole county for the U.S.; it obligates us to search a city. Additionally, the API has a limit of 50 queries. Thus, we will collect the top 20 most popular food establishments of (or near) the most populated city of each of the 83 counties in the state of Michigan. We will search with "food" as the term of interest and the "location" as the most populated area within the specific county. Then, we will append all 83 datasets to have a full dataset of the most popular food establishments, cuisine type of each food establishment, and city (or nearby city) of each food establishment for the state of Michigan.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;The data from Yelp provides us information regarding location (city, state, longtitude, latitude). However, we are interested in studying counties within the state of Michigan. Thus, we will create an object that will provide us with the food establishment's county, mapped from its corresponding city. We will show an example of this using Wayne County.

```{r}
#search url and collect data per county
yelp <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=detroit+MI" #wayne
url <- modify_url(yelp, path = c("v3", "businesses", "search"))
res <- GET(url, add_headers('Authorization' = paste("bearer", client_secret)))
results <- content(res)

#parse data
yelp_httr_parse <- function(x) {

  parse_list <- list(id = x$id, 
                     name = x$name, 
                     categories = x$categories, 
                     rating = x$rating, 
                     review_count = x$review_count, 
                     latitude = x$coordinates$latitude, 
                     longitude = x$coordinates$longitude, 
                     address1 = x$location$address1, 
                     city = x$location$city, 
                     state = x$location$state, 
                     distance = x$distance)
  
  parse_list <- lapply(parse_list, FUN = function(x) ifelse(is.null(x), "", x))
  
  df <- tibble(id=parse_list$id,
                   name=parse_list$name, 
                   categories = parse_list$categories, 
                   rating = parse_list$rating, 
                   review_count = parse_list$review_count, 
                   latitude=parse_list$latitude, 
                   longitude = parse_list$longitude, 
                   address1 = parse_list$address1, 
                   city = parse_list$city, 
                   state = parse_list$state, 
                   distance= parse_list$distance)
  df
}

results_list <- lapply(results$businesses, FUN = yelp_httr_parse)
food <- do.call("rbind", results_list)
county <- rep("Wayne",length(food$city))
food_data <- cbind(food, county)
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Now, this process will be repeated for the remaining 82 counties of Michigan.

```{r, include = FALSE}
#search url and collect data per county
yelp2 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=troy+MI" #oakland
yelp3 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=warren+MI" #macomb
yelp4 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=grand+rapids+MI" #kent
yelp5 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=flint+MI" #genesee
yelp6 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ann+arbor+MI" #washtenaw
yelp7 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=lansing+MI" #ingham
yelp8 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=allendale+MI" #ottawa
yelp9 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=kalamazoo+MI" #kalamazoo
yelp10 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=howell+MI" #livingston
yelp11 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=saginaw+MI" #saginaw
yelp12 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=muskegon+MI" #muskegon
yelp13 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=port+huron+MI" #st. clair
yelp14 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=jackson+MI" #jackson
yelp15 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=niles+MI" #berrien
yelp16 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=monroe+MI" #monroe
yelp17 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=battle+creek+MI" #calhoun
yelp18 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=holland+MI" #allegan
yelp19 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=charlotte+MI" #eaton
yelp20 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=bay+city+MI" #bay
yelp21 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=adrian+MI" #lenawee
yelp22 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=traverse+city+MI" #grand traverse
yelp23 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=lapeer+MI" #lapeer
yelp24 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=midland+MI" #midland
yelp25 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=saint+johns+MI" #clinton
yelp26 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=south+haven+MI" #van buren
yelp27 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=mount+pleasant+MI" #isabella
yelp28 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=owosso+MI" #shiawassee
yelp29 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=marquette+MI" #marquette
yelp30 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ionia+MI" #ionia
yelp31 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=greenville+MI" #montcalm
yelp32 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=hastings+MI" #barry
yelp33 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=sturgis+MI" #st. joseph
yelp34 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=caro+MI" #tuscola
yelp35 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=dowagiac+MI" #cass
yelp36 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=fremont+MI" #newaygo
yelp37 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=hillsdale+MI" #hillsdale
yelp38 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=coldwater+MI" #branch
yelp39 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=big+rapids+MI" #mecosta
yelp40 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=sandusky+MI" #sanilac
yelp41 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=alma+MI" #gratiot
yelp42 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=sault+ste+marie+MI" #chippewa
yelp43 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=hancock+MI" #houghton
yelp44 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=escanaba+MI" #delta
yelp45 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=cadillac+MI" #wexford
yelp46 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=petosky+MI" #emmet
yelp47 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=bad+axe+MI" #huron
yelp48 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=clare+MI" #clare
yelp49 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ludington+MI" #mason
yelp50 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=alpena+MI" #alpena
yelp51 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=hart+MI" #oceana
yelp52 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=boyne+city+MI" #charlevoix
yelp53 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=cheboygan+MI" #cheboygan
yelp54 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=iron+mountain+MI" #dickinson
yelp55 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=gladwin+MI" #gladwin
yelp56 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=east+tawas+MI" #iosco
yelp57 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=gaylord+MI" #otsego
yelp58 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=manistee+MI" #manistee
yelp59 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=roscommon+MI" #roscommon
yelp60 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=elk+rapids+MI" #antrim
yelp61 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=reed+city+MI" #osceola
yelp62 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=menominee+MI" #menominee
yelp63 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=greilickville+MI" #leelanau
yelp64 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=west+branch+MI" #ogemaw
yelp65 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=kalkaska+MI" #kalkaska
yelp66 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=frankfort+MI" #benzie
yelp67 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=lake+city+MI" #missaukee
yelp68 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ironwood+MI" #gogebic
yelp69 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=standish+MI" #arenac
yelp70 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=grayling+MI" #crawford
yelp71 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=rogers+city+MI" #presque isle
yelp72 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=baldwin+MI" #lake
yelp73 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=iron+river+MI" #iron
yelp74 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=st+ignace+MI" #mackinac
yelp75 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=harrisville+MI" #alcona
yelp76 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=hillman+MI" #montmorency
yelp77 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=munising+MI" #alger
yelp78 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=baraga+MI" #baraga
yelp79 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=big+creek+township+MI" #oscoda
yelp80 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=manistique+MI" #schoolcraft
yelp81 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=newberry+MI" #luce
yelp82 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ontonagon+MI" #ontonagon
yelp83 <- "https://api.yelp.com/v3/businesses/search/?limit=20&offset=0&sort=0&term=food&location=ahmeek+MI" #keweenaw

url2 <- modify_url(yelp2, path = c("v3", "businesses", "search"))
url3 <- modify_url(yelp3, path = c("v3", "businesses", "search"))
url4 <- modify_url(yelp4, path = c("v3", "businesses", "search"))
url5 <- modify_url(yelp5, path = c("v3", "businesses", "search"))
url6 <- modify_url(yelp6, path = c("v3", "businesses", "search"))
url7 <- modify_url(yelp7, path = c("v3", "businesses", "search"))
url8 <- modify_url(yelp8, path = c("v3", "businesses", "search"))
url9 <- modify_url(yelp9, path = c("v3", "businesses", "search"))
url10 <- modify_url(yelp10, path = c("v3", "businesses", "search"))
url11 <- modify_url(yelp11, path = c("v3", "businesses", "search"))
url12 <- modify_url(yelp12, path = c("v3", "businesses", "search"))
url13 <- modify_url(yelp13, path = c("v3", "businesses", "search"))
url14 <- modify_url(yelp14, path = c("v3", "businesses", "search"))
url15 <- modify_url(yelp15, path = c("v3", "businesses", "search"))
url16 <- modify_url(yelp16, path = c("v3", "businesses", "search"))
url17 <- modify_url(yelp17, path = c("v3", "businesses", "search"))
url18 <- modify_url(yelp18, path = c("v3", "businesses", "search"))
url19 <- modify_url(yelp19, path = c("v3", "businesses", "search"))
url20 <- modify_url(yelp20, path = c("v3", "businesses", "search"))
url21 <- modify_url(yelp21, path = c("v3", "businesses", "search"))
url22 <- modify_url(yelp22, path = c("v3", "businesses", "search"))
url23 <- modify_url(yelp23, path = c("v3", "businesses", "search"))
url24 <- modify_url(yelp24, path = c("v3", "businesses", "search"))
url25 <- modify_url(yelp25, path = c("v3", "businesses", "search"))
url26 <- modify_url(yelp26, path = c("v3", "businesses", "search"))
url27 <- modify_url(yelp27, path = c("v3", "businesses", "search"))
url28 <- modify_url(yelp28, path = c("v3", "businesses", "search"))
url29 <- modify_url(yelp29, path = c("v3", "businesses", "search"))
url30 <- modify_url(yelp30, path = c("v3", "businesses", "search"))
url31 <- modify_url(yelp31, path = c("v3", "businesses", "search"))
url32 <- modify_url(yelp32, path = c("v3", "businesses", "search"))
url33 <- modify_url(yelp33, path = c("v3", "businesses", "search"))
url34 <- modify_url(yelp34, path = c("v3", "businesses", "search"))
url35 <- modify_url(yelp35, path = c("v3", "businesses", "search"))
url36 <- modify_url(yelp36, path = c("v3", "businesses", "search"))
url37 <- modify_url(yelp37, path = c("v3", "businesses", "search"))
url38 <- modify_url(yelp38, path = c("v3", "businesses", "search"))
url39 <- modify_url(yelp39, path = c("v3", "businesses", "search"))
url40 <- modify_url(yelp40, path = c("v3", "businesses", "search"))
url41 <- modify_url(yelp41, path = c("v3", "businesses", "search"))
url42 <- modify_url(yelp42, path = c("v3", "businesses", "search"))
url43 <- modify_url(yelp43, path = c("v3", "businesses", "search"))
url44 <- modify_url(yelp44, path = c("v3", "businesses", "search"))
url45 <- modify_url(yelp45, path = c("v3", "businesses", "search"))
url46 <- modify_url(yelp46, path = c("v3", "businesses", "search"))
url47 <- modify_url(yelp47, path = c("v3", "businesses", "search"))
url48 <- modify_url(yelp48, path = c("v3", "businesses", "search"))
url49 <- modify_url(yelp49, path = c("v3", "businesses", "search"))
url50 <- modify_url(yelp50, path = c("v3", "businesses", "search"))
url51 <- modify_url(yelp51, path = c("v3", "businesses", "search"))
url52 <- modify_url(yelp52, path = c("v3", "businesses", "search"))
url53 <- modify_url(yelp53, path = c("v3", "businesses", "search"))
url54 <- modify_url(yelp54, path = c("v3", "businesses", "search"))
url55 <- modify_url(yelp55, path = c("v3", "businesses", "search"))
url56 <- modify_url(yelp56, path = c("v3", "businesses", "search"))
url57 <- modify_url(yelp57, path = c("v3", "businesses", "search"))
url58 <- modify_url(yelp58, path = c("v3", "businesses", "search"))
url59 <- modify_url(yelp59, path = c("v3", "businesses", "search"))
url60 <- modify_url(yelp60, path = c("v3", "businesses", "search"))
url61 <- modify_url(yelp61, path = c("v3", "businesses", "search"))
url62 <- modify_url(yelp62, path = c("v3", "businesses", "search"))
url63 <- modify_url(yelp63, path = c("v3", "businesses", "search"))
url64 <- modify_url(yelp64, path = c("v3", "businesses", "search"))
url65 <- modify_url(yelp65, path = c("v3", "businesses", "search"))
url66 <- modify_url(yelp66, path = c("v3", "businesses", "search"))
url67 <- modify_url(yelp67, path = c("v3", "businesses", "search"))
url68 <- modify_url(yelp68, path = c("v3", "businesses", "search"))
url69 <- modify_url(yelp69, path = c("v3", "businesses", "search"))
url70 <- modify_url(yelp70, path = c("v3", "businesses", "search"))
url71 <- modify_url(yelp71, path = c("v3", "businesses", "search"))
url72 <- modify_url(yelp72, path = c("v3", "businesses", "search"))
url73 <- modify_url(yelp73, path = c("v3", "businesses", "search"))
url74 <- modify_url(yelp74, path = c("v3", "businesses", "search"))
url75 <- modify_url(yelp75, path = c("v3", "businesses", "search"))
url76 <- modify_url(yelp76, path = c("v3", "businesses", "search"))
url77 <- modify_url(yelp77, path = c("v3", "businesses", "search"))
url78 <- modify_url(yelp78, path = c("v3", "businesses", "search"))
url79 <- modify_url(yelp79, path = c("v3", "businesses", "search"))
url80 <- modify_url(yelp80, path = c("v3", "businesses", "search"))
url81 <- modify_url(yelp81, path = c("v3", "businesses", "search"))
url82 <- modify_url(yelp82, path = c("v3", "businesses", "search"))
url83 <- modify_url(yelp83, path = c("v3", "businesses", "search"))

res2 <- GET(url2, add_headers('Authorization' = paste("bearer", client_secret)))
res3 <- GET(url3, add_headers('Authorization' = paste("bearer", client_secret)))
res4 <- GET(url4, add_headers('Authorization' = paste("bearer", client_secret)))
res5 <- GET(url5, add_headers('Authorization' = paste("bearer", client_secret)))
res6 <- GET(url6, add_headers('Authorization' = paste("bearer", client_secret)))
res7 <- GET(url7, add_headers('Authorization' = paste("bearer", client_secret)))
res8 <- GET(url8, add_headers('Authorization' = paste("bearer", client_secret)))
res9 <- GET(url9, add_headers('Authorization' = paste("bearer", client_secret)))
res10 <- GET(url10, add_headers('Authorization' = paste("bearer", client_secret)))
res11 <- GET(url11, add_headers('Authorization' = paste("bearer", client_secret)))
res12 <- GET(url12, add_headers('Authorization' = paste("bearer", client_secret)))
res13 <- GET(url13, add_headers('Authorization' = paste("bearer", client_secret)))
res14 <- GET(url14, add_headers('Authorization' = paste("bearer", client_secret)))
res15 <- GET(url15, add_headers('Authorization' = paste("bearer", client_secret)))
res16 <- GET(url16, add_headers('Authorization' = paste("bearer", client_secret)))
res17 <- GET(url17, add_headers('Authorization' = paste("bearer", client_secret)))
res18 <- GET(url18, add_headers('Authorization' = paste("bearer", client_secret)))
res19 <- GET(url19, add_headers('Authorization' = paste("bearer", client_secret)))
res20 <- GET(url20, add_headers('Authorization' = paste("bearer", client_secret)))
res21 <- GET(url21, add_headers('Authorization' = paste("bearer", client_secret)))
res22 <- GET(url22, add_headers('Authorization' = paste("bearer", client_secret)))
res23 <- GET(url23, add_headers('Authorization' = paste("bearer", client_secret)))
res24 <- GET(url24, add_headers('Authorization' = paste("bearer", client_secret)))
res25 <- GET(url25, add_headers('Authorization' = paste("bearer", client_secret)))
res26 <- GET(url26, add_headers('Authorization' = paste("bearer", client_secret)))
res27 <- GET(url27, add_headers('Authorization' = paste("bearer", client_secret)))
res28 <- GET(url28, add_headers('Authorization' = paste("bearer", client_secret)))
res29 <- GET(url29, add_headers('Authorization' = paste("bearer", client_secret)))
res30 <- GET(url30, add_headers('Authorization' = paste("bearer", client_secret)))
res31 <- GET(url31, add_headers('Authorization' = paste("bearer", client_secret)))
res32 <- GET(url32, add_headers('Authorization' = paste("bearer", client_secret)))
res33 <- GET(url33, add_headers('Authorization' = paste("bearer", client_secret)))
res34 <- GET(url34, add_headers('Authorization' = paste("bearer", client_secret)))
res35 <- GET(url35, add_headers('Authorization' = paste("bearer", client_secret)))
res36 <- GET(url36, add_headers('Authorization' = paste("bearer", client_secret)))
res37 <- GET(url37, add_headers('Authorization' = paste("bearer", client_secret)))
res38 <- GET(url38, add_headers('Authorization' = paste("bearer", client_secret)))
res39 <- GET(url39, add_headers('Authorization' = paste("bearer", client_secret)))
res40 <- GET(url40, add_headers('Authorization' = paste("bearer", client_secret)))
res41 <- GET(url41, add_headers('Authorization' = paste("bearer", client_secret)))
res42 <- GET(url42, add_headers('Authorization' = paste("bearer", client_secret)))
res43 <- GET(url43, add_headers('Authorization' = paste("bearer", client_secret)))
res44 <- GET(url44, add_headers('Authorization' = paste("bearer", client_secret)))
res45 <- GET(url45, add_headers('Authorization' = paste("bearer", client_secret)))
res46 <- GET(url46, add_headers('Authorization' = paste("bearer", client_secret)))
res47 <- GET(url47, add_headers('Authorization' = paste("bearer", client_secret)))
res48 <- GET(url48, add_headers('Authorization' = paste("bearer", client_secret)))
res49 <- GET(url49, add_headers('Authorization' = paste("bearer", client_secret)))
res50 <- GET(url50, add_headers('Authorization' = paste("bearer", client_secret)))
res51 <- GET(url51, add_headers('Authorization' = paste("bearer", client_secret)))
res52 <- GET(url52, add_headers('Authorization' = paste("bearer", client_secret)))
res53 <- GET(url53, add_headers('Authorization' = paste("bearer", client_secret)))
res54 <- GET(url54, add_headers('Authorization' = paste("bearer", client_secret)))
res55 <- GET(url55, add_headers('Authorization' = paste("bearer", client_secret)))
res56 <- GET(url56, add_headers('Authorization' = paste("bearer", client_secret)))
res57 <- GET(url57, add_headers('Authorization' = paste("bearer", client_secret)))
res58 <- GET(url58, add_headers('Authorization' = paste("bearer", client_secret)))
res59 <- GET(url59, add_headers('Authorization' = paste("bearer", client_secret)))
res60 <- GET(url60, add_headers('Authorization' = paste("bearer", client_secret)))
res61 <- GET(url61, add_headers('Authorization' = paste("bearer", client_secret)))
res62 <- GET(url62, add_headers('Authorization' = paste("bearer", client_secret)))
res63 <- GET(url63, add_headers('Authorization' = paste("bearer", client_secret)))
res64 <- GET(url64, add_headers('Authorization' = paste("bearer", client_secret)))
res65 <- GET(url65, add_headers('Authorization' = paste("bearer", client_secret)))
res66 <- GET(url66, add_headers('Authorization' = paste("bearer", client_secret)))
res67 <- GET(url67, add_headers('Authorization' = paste("bearer", client_secret)))
res68 <- GET(url68, add_headers('Authorization' = paste("bearer", client_secret)))
res69 <- GET(url69, add_headers('Authorization' = paste("bearer", client_secret)))
res70 <- GET(url70, add_headers('Authorization' = paste("bearer", client_secret)))
res71 <- GET(url71, add_headers('Authorization' = paste("bearer", client_secret)))
res72 <- GET(url72, add_headers('Authorization' = paste("bearer", client_secret)))
res73 <- GET(url73, add_headers('Authorization' = paste("bearer", client_secret)))
res74 <- GET(url74, add_headers('Authorization' = paste("bearer", client_secret)))
res75 <- GET(url75, add_headers('Authorization' = paste("bearer", client_secret)))
res76 <- GET(url76, add_headers('Authorization' = paste("bearer", client_secret)))
res77 <- GET(url77, add_headers('Authorization' = paste("bearer", client_secret)))
res78 <- GET(url78, add_headers('Authorization' = paste("bearer", client_secret)))
res79 <- GET(url79, add_headers('Authorization' = paste("bearer", client_secret)))
res80 <- GET(url80, add_headers('Authorization' = paste("bearer", client_secret)))
res81 <- GET(url81, add_headers('Authorization' = paste("bearer", client_secret)))
res82 <- GET(url82, add_headers('Authorization' = paste("bearer", client_secret)))
res83 <- GET(url83, add_headers('Authorization' = paste("bearer", client_secret)))

results2 <- content(res2)
results3 <- content(res3)
results4 <- content(res4)
results5 <- content(res5)
results6 <- content(res6)
results7 <- content(res7)
results8 <- content(res8)
results9 <- content(res9)
results10 <- content(res10)
results11 <- content(res11)
results12 <- content(res12)
results13 <- content(res13)
results14 <- content(res14)
results15 <- content(res15)
results16 <- content(res16)
results17 <- content(res17)
results18 <- content(res18)
results19 <- content(res19)
results20 <- content(res20)
results21 <- content(res21)
results22 <- content(res22)
results23 <- content(res23)
results24 <- content(res24)
results25 <- content(res25)
results26 <- content(res26)
results27 <- content(res27)
results28 <- content(res28)
results29 <- content(res29)
results30 <- content(res30)
results31 <- content(res31)
results32 <- content(res32)
results33 <- content(res33)
results34 <- content(res34)
results35 <- content(res35)
results36 <- content(res36)
results37 <- content(res37)
results38 <- content(res38)
results39 <- content(res39)
results40 <- content(res40)
results41 <- content(res41)
results42 <- content(res42)
results43 <- content(res43)
results44 <- content(res44)
results45 <- content(res45)
results46 <- content(res46)
results47 <- content(res47)
results48 <- content(res48)
results49 <- content(res49)
results50 <- content(res50)
results51 <- content(res51)
results52 <- content(res52)
results53 <- content(res53)
results54 <- content(res54)
results55 <- content(res55)
results56 <- content(res56)
results57 <- content(res57)
results58 <- content(res58)
results59 <- content(res59)
results60 <- content(res60)
results61 <- content(res61)
results62 <- content(res62)
results63 <- content(res63)
results64 <- content(res64)
results65 <- content(res65)
results66 <- content(res66)
results67 <- content(res67)
results68 <- content(res68)
results69 <- content(res69)
results70 <- content(res70)
results71 <- content(res71)
results72 <- content(res72)
results73 <- content(res73)
results74 <- content(res74)
results75 <- content(res75)
results76 <- content(res76)
results77 <- content(res77)
results78 <- content(res78)
results79 <- content(res79)
results80 <- content(res80)
results81 <- content(res81)
results82 <- content(res82)
results83 <- content(res83)

#parse data
yelp_httr_parse <- function(x) {

  parse_list <- list(id = x$id, 
                     name = x$name, 
                     categories = x$categories, 
                     rating = x$rating, 
                     review_count = x$review_count, 
                     latitude = x$coordinates$latitude, 
                     longitude = x$coordinates$longitude, 
                     address1 = x$location$address1, 
                     city = x$location$city, 
                     state = x$location$state, 
                     distance = x$distance)
  
  parse_list <- lapply(parse_list, FUN = function(x) ifelse(is.null(x), "", x))
  
  df <- tibble(id=parse_list$id,
                   name=parse_list$name, 
                   categories = parse_list$categories, 
                   rating = parse_list$rating, 
                   review_count = parse_list$review_count, 
                   latitude=parse_list$latitude, 
                   longitude = parse_list$longitude, 
                   address1 = parse_list$address1, 
                   city = parse_list$city, 
                   state = parse_list$state, 
                   distance= parse_list$distance)
  df
}

results_list2 <- lapply(results2$businesses, FUN = yelp_httr_parse)
results_list3 <- lapply(results3$businesses, FUN = yelp_httr_parse)
results_list4 <- lapply(results4$businesses, FUN = yelp_httr_parse)
results_list5 <- lapply(results5$businesses, FUN = yelp_httr_parse)
results_list6 <- lapply(results6$businesses, FUN = yelp_httr_parse)
results_list7 <- lapply(results7$businesses, FUN = yelp_httr_parse)
results_list8 <- lapply(results8$businesses, FUN = yelp_httr_parse)
results_list9 <- lapply(results9$businesses, FUN = yelp_httr_parse)
results_list10 <- lapply(results10$businesses, FUN = yelp_httr_parse)
results_list11 <- lapply(results11$businesses, FUN = yelp_httr_parse)
results_list12 <- lapply(results12$businesses, FUN = yelp_httr_parse)
results_list13 <- lapply(results13$businesses, FUN = yelp_httr_parse)
results_list14 <- lapply(results14$businesses, FUN = yelp_httr_parse)
results_list15 <- lapply(results15$businesses, FUN = yelp_httr_parse)
results_list16 <- lapply(results16$businesses, FUN = yelp_httr_parse)
results_list17 <- lapply(results17$businesses, FUN = yelp_httr_parse)
results_list18 <- lapply(results18$businesses, FUN = yelp_httr_parse)
results_list19 <- lapply(results19$businesses, FUN = yelp_httr_parse)
results_list20 <- lapply(results20$businesses, FUN = yelp_httr_parse)
results_list21 <- lapply(results21$businesses, FUN = yelp_httr_parse)
results_list22 <- lapply(results22$businesses, FUN = yelp_httr_parse)
results_list23 <- lapply(results23$businesses, FUN = yelp_httr_parse)
results_list24 <- lapply(results24$businesses, FUN = yelp_httr_parse)
results_list25 <- lapply(results25$businesses, FUN = yelp_httr_parse)
results_list26 <- lapply(results26$businesses, FUN = yelp_httr_parse)
results_list27 <- lapply(results27$businesses, FUN = yelp_httr_parse)
results_list28 <- lapply(results28$businesses, FUN = yelp_httr_parse)
results_list29 <- lapply(results29$businesses, FUN = yelp_httr_parse)
results_list30 <- lapply(results30$businesses, FUN = yelp_httr_parse)
results_list31 <- lapply(results31$businesses, FUN = yelp_httr_parse)
results_list32 <- lapply(results32$businesses, FUN = yelp_httr_parse)
results_list33 <- lapply(results33$businesses, FUN = yelp_httr_parse)
results_list34 <- lapply(results34$businesses, FUN = yelp_httr_parse)
results_list35 <- lapply(results35$businesses, FUN = yelp_httr_parse)
results_list36 <- lapply(results36$businesses, FUN = yelp_httr_parse)
results_list37 <- lapply(results37$businesses, FUN = yelp_httr_parse)
results_list38 <- lapply(results38$businesses, FUN = yelp_httr_parse)
results_list39 <- lapply(results39$businesses, FUN = yelp_httr_parse)
results_list40 <- lapply(results40$businesses, FUN = yelp_httr_parse)
results_list41 <- lapply(results41$businesses, FUN = yelp_httr_parse)
results_list42 <- lapply(results42$businesses, FUN = yelp_httr_parse)
results_list43 <- lapply(results43$businesses, FUN = yelp_httr_parse)
results_list44 <- lapply(results44$businesses, FUN = yelp_httr_parse)
results_list45 <- lapply(results45$businesses, FUN = yelp_httr_parse)
results_list46 <- lapply(results46$businesses, FUN = yelp_httr_parse)
results_list47 <- lapply(results47$businesses, FUN = yelp_httr_parse)
results_list48 <- lapply(results48$businesses, FUN = yelp_httr_parse)
results_list49 <- lapply(results49$businesses, FUN = yelp_httr_parse)
results_list50 <- lapply(results50$businesses, FUN = yelp_httr_parse)
results_list51 <- lapply(results51$businesses, FUN = yelp_httr_parse)
results_list52 <- lapply(results52$businesses, FUN = yelp_httr_parse)
results_list53 <- lapply(results53$businesses, FUN = yelp_httr_parse)
results_list54 <- lapply(results54$businesses, FUN = yelp_httr_parse)
results_list55 <- lapply(results55$businesses, FUN = yelp_httr_parse)
results_list56 <- lapply(results56$businesses, FUN = yelp_httr_parse)
results_list57 <- lapply(results57$businesses, FUN = yelp_httr_parse)
results_list58 <- lapply(results58$businesses, FUN = yelp_httr_parse)
results_list59 <- lapply(results59$businesses, FUN = yelp_httr_parse)
results_list60 <- lapply(results60$businesses, FUN = yelp_httr_parse)
results_list61 <- lapply(results61$businesses, FUN = yelp_httr_parse)
results_list62 <- lapply(results62$businesses, FUN = yelp_httr_parse)
results_list63 <- lapply(results63$businesses, FUN = yelp_httr_parse)
results_list64 <- lapply(results64$businesses, FUN = yelp_httr_parse)
results_list65 <- lapply(results65$businesses, FUN = yelp_httr_parse)
results_list66 <- lapply(results66$businesses, FUN = yelp_httr_parse)
results_list67 <- lapply(results67$businesses, FUN = yelp_httr_parse)
results_list68 <- lapply(results68$businesses, FUN = yelp_httr_parse)
results_list69 <- lapply(results69$businesses, FUN = yelp_httr_parse)
results_list70 <- lapply(results70$businesses, FUN = yelp_httr_parse)
results_list71 <- lapply(results71$businesses, FUN = yelp_httr_parse)
results_list72 <- lapply(results72$businesses, FUN = yelp_httr_parse)
results_list73 <- lapply(results73$businesses, FUN = yelp_httr_parse)
results_list74 <- lapply(results74$businesses, FUN = yelp_httr_parse)
results_list75 <- lapply(results75$businesses, FUN = yelp_httr_parse)
results_list76 <- lapply(results76$businesses, FUN = yelp_httr_parse)
results_list77 <- lapply(results77$businesses, FUN = yelp_httr_parse)
results_list78 <- lapply(results78$businesses, FUN = yelp_httr_parse)
results_list79 <- lapply(results79$businesses, FUN = yelp_httr_parse)
results_list80 <- lapply(results80$businesses, FUN = yelp_httr_parse)
results_list81 <- lapply(results81$businesses, FUN = yelp_httr_parse)
results_list82 <- lapply(results82$businesses, FUN = yelp_httr_parse)
results_list83 <- lapply(results83$businesses, FUN = yelp_httr_parse)

food2 <- do.call("rbind", results_list2)
county <- rep("Oakland", length(food2$city))
food_data2 <- cbind(food2, county)

food3 <- do.call("rbind", results_list3)
county <- rep("Macomb", length(food3$city))
food_data3 <- cbind(food3, county)

food4 <- do.call("rbind", results_list4)
county <- rep("Kent", length(food4$city))
food_data4 <- cbind(food4, county)

food5 <- do.call("rbind", results_list5)
county <- rep("Genesee", length(food5$city))
food_data5 <- cbind(food5, county)

food6 <- do.call("rbind", results_list6)
county <- rep("Washtenaw", length(food6$city))
food_data6 <- cbind(food6, county)

food7 <- do.call("rbind", results_list7)
county <- rep("Ingham", length(food7$city))
food_data7 <- cbind(food7, county)

food8 <- do.call("rbind", results_list8)
county <- rep("Ottawa", length(food8$city))
food_data8 <- cbind(food8, county)

food9 <- do.call("rbind", results_list9)
county <- rep("Kalamazoo", length(food9$city))
food_data9 <- cbind(food9, county)

food10 <- do.call("rbind", results_list10)
county <- rep("Livingston", length(food10$city))
food_data10 <- cbind(food10, county)

food11 <- do.call("rbind", results_list11)
county <- rep("Saginaw", length(food11$city))
food_data11 <- cbind(food11, county)

food12 <- do.call("rbind", results_list12)
county <- rep("Muskegon", length(food12$city))
food_data12 <- cbind(food12, county)

food13 <- do.call("rbind", results_list13)
county <- rep("St. Clair", length(food13$city))
food_data13 <- cbind(food13, county)

food14 <- do.call("rbind", results_list14)
county <- rep("Jackson", length(food14$city))
food_data14 <- cbind(food14, county)

food15 <- do.call("rbind", results_list15)
county <- rep("Berrien", length(food15$city))
food_data15 <- cbind(food15, county)

food16 <- do.call("rbind", results_list16)
county <- rep("Monroe", length(food16$city))
food_data16 <- cbind(food16, county)

food17 <- do.call("rbind", results_list17)
county <- rep("Calhoun", length(food17$city))
food_data17 <- cbind(food17, county)

food18 <- do.call("rbind", results_list18)
county <- rep("Allegan", length(food18$city))
food_data18 <- cbind(food18, county)

food19 <- do.call("rbind", results_list19)
county <- rep("Eaton", length(food19$city))
food_data19 <- cbind(food19, county)

food20 <- do.call("rbind", results_list20)
county <- rep("Bay", length(food20$city))
food_data20 <- cbind(food20, county)

food21 <- do.call("rbind", results_list21)
county <- rep("Lenawee", length(food21$city))
food_data21 <- cbind(food21, county)

food22 <- do.call("rbind", results_list22)
county <- rep("Grand Traverse", length(food22$city))
food_data22 <- cbind(food22, county)

food23 <- do.call("rbind", results_list23)
county <- rep("Lapeer", length(food23$city))
food_data23 <- cbind(food23, county)

food24 <- do.call("rbind", results_list24)
county <- rep("Midland", length(food24$city))
food_data24 <- cbind(food24, county)

food25 <- do.call("rbind", results_list25)
county <- rep("Clinton", length(food25$city))
food_data25 <- cbind(food25, county)

food26 <- do.call("rbind", results_list26)
county <- rep("Van Buren", length(food26$city))
food_data26 <- cbind(food26, county)

food27 <- do.call("rbind", results_list27)
county <- rep("Isabella", length(food27$city))
food_data27 <- cbind(food27, county)

food28 <- do.call("rbind", results_list28)
county <- rep("Shiawassee", length(food28$city))
food_data28 <- cbind(food28, county)

food29 <- do.call("rbind", results_list29)
county <- rep("Marquette", length(food29$city))
food_data29 <- cbind(food29, county)

food30 <- do.call("rbind", results_list30)
county <- rep("Ionia", length(food30$city))
food_data30 <- cbind(food30, county)

food31 <- do.call("rbind", results_list31)
county <- rep("Montcalm", length(food31$city))
food_data31 <- cbind(food31, county)

food32 <- do.call("rbind", results_list32)
county <- rep("Barry", length(food32$city))
food_data32 <- cbind(food32, county)

food33 <- do.call("rbind", results_list33)
county <- rep("St. Joseph", length(food33$city))
food_data33 <- cbind(food33, county)

food34 <- do.call("rbind", results_list34)
county <- rep("Tuscola", length(food34$city))
food_data34 <- cbind(food34, county)

food35 <- do.call("rbind", results_list35)
county <- rep("Cass", length(food35$city))
food_data35 <- cbind(food35, county)

food36 <- do.call("rbind", results_list36)
county <- rep("Newaygo", length(food36$city))
food_data36 <- cbind(food36, county)

food37 <- do.call("rbind", results_list37)
county <- rep("Hillsdale", length(food37$city))
food_data37 <- cbind(food37, county)

food38 <- do.call("rbind", results_list38)
county <- rep("Branch", length(food38$city))
food_data38 <- cbind(food38, county)

food39 <- do.call("rbind", results_list39)
county <- rep("Mecosta", length(food39$city))
food_data39 <- cbind(food39, county)

food40 <- do.call("rbind", results_list40)
county <- rep("Sanilac", length(food40$city))
food_data40 <- cbind(food40, county)

food41 <- do.call("rbind", results_list41)
county <- rep("Gratiot", length(food41$city))
food_data41 <- cbind(food41, county)

food42 <- do.call("rbind", results_list42)
county <- rep("Chippewa", length(food42$city))
food_data42 <- cbind(food42, county)

food43 <- do.call("rbind", results_list43)
county <- rep("Houghton", length(food43$city))
food_data43 <- cbind(food43, county)

food44 <- do.call("rbind", results_list44)
county <- rep("Delta", length(food44$city))
food_data44 <- cbind(food44, county)

food45 <- do.call("rbind", results_list45)
county <- rep("Wexford", length(food45$city))
food_data45 <- cbind(food45, county)

food46 <- do.call("rbind", results_list46)
county <- rep("Emmet", length(food46$city))
food_data46 <- cbind(food46, county)

food47 <- do.call("rbind", results_list47)
county <- rep("Huron", length(food47$city))
food_data47 <- cbind(food47, county)

food48 <- do.call("rbind", results_list48)
county <- rep("Clare", length(food48$city))
food_data48 <- cbind(food48, county)

food49 <- do.call("rbind", results_list49)
county <- rep("Mason", length(food49$city))
food_data49 <- cbind(food49, county)

food50 <- do.call("rbind", results_list50)
county <- rep("Alpena", length(food50$city))
food_data50 <- cbind(food50, county)

food51 <- do.call("rbind", results_list51)
county <- rep("Oceana", length(food51$city))
food_data51 <- cbind(food51, county)

food52 <- do.call("rbind", results_list52)
county <- rep("Charlevoix", length(food52$city))
food_data52 <- cbind(food52, county)

food53 <- do.call("rbind", results_list53)
county <- rep("Cheboygan", length(food53$city))
food_data53 <- cbind(food53, county)

food54 <- do.call("rbind", results_list54)
county <- rep("Dickinson", length(food54$city))
food_data54 <- cbind(food54, county)

food55 <- do.call("rbind", results_list55)
county <- rep("Gladwin", length(food55$city))
food_data55 <- cbind(food55, county)

food56 <- do.call("rbind", results_list56)
county <- rep("Iosco", length(food56$city))
food_data56 <- cbind(food56, county)

food57 <- do.call("rbind", results_list57)
county <- rep("Otsego", length(food57$city))
food_data57 <- cbind(food57, county)

food58 <- do.call("rbind", results_list58)
county <- rep("Manistee", length(food58$city))
food_data58 <- cbind(food58, county)

food59 <- do.call("rbind", results_list59)
county <- rep("Roscommon", length(food59$city))
food_data59 <- cbind(food59, county)

food60 <- do.call("rbind", results_list60)
county <- rep("Antrim", length(food60$city))
food_data60 <- cbind(food60, county)

food61 <- do.call("rbind", results_list61)
county <- rep("Osceola", length(food61$city))
food_data61 <- cbind(food61, county)

food62 <- do.call("rbind", results_list62)
county <- rep("Menominee", length(food62$city))
food_data62 <- cbind(food62, county)

food63 <- do.call("rbind", results_list63)
county <- rep("Leelanau", length(food63$city))
food_data63 <- cbind(food63, county)

food64 <- do.call("rbind", results_list64)
county <- rep("Ogemaw", length(food64$city))
food_data64 <- cbind(food64, county)

food65 <- do.call("rbind", results_list65)
county <- rep("Kalkaska", length(food65$city))
food_data65 <- cbind(food65, county)

food66 <- do.call("rbind", results_list66)
county <- rep("Benzie", length(food66$city))
food_data66 <- cbind(food66, county)

food67 <- do.call("rbind", results_list67)
county <- rep("Missaukee", length(food67$city))
food_data67 <- cbind(food67, county)

food68 <- do.call("rbind", results_list68)
county <- rep("Gogebic", length(food68$city))
food_data68 <- cbind(food68, county)

food69 <- do.call("rbind", results_list69)
county <- rep("Arenac", length(food69$city))
food_data69 <- cbind(food69, county)

food70 <- do.call("rbind", results_list70)
county <- rep("Crawford", length(food70$city))
food_data70 <- cbind(food70, county)

food71 <- do.call("rbind", results_list71)
county <- rep("Presque Isle", length(food71$city))
food_data71 <- cbind(food71, county)

food72 <- do.call("rbind", results_list72)
county <- rep("Lake", length(food72$city))
food_data72 <- cbind(food72, county)

food73 <- do.call("rbind", results_list73)
county <- rep("Iron", length(food73$city))
food_data73 <- cbind(food73, county)

food74 <- do.call("rbind", results_list74)
county <- rep("Mackinac", length(food74$city))
food_data74 <- cbind(food74, county)

food75 <- do.call("rbind", results_list75)
county <- rep("Alcona", length(food75$city))
food_data75 <- cbind(food75, county)

food76 <- do.call("rbind", results_list76)
county <- rep("Montmorency", length(food76$city))
food_data76 <- cbind(food76, county)

food77 <- do.call("rbind", results_list77)
county <- rep("Alger", length(food77$city))
food_data77 <- cbind(food77, county)

food78 <- do.call("rbind", results_list78)
county <- rep("Baraga", length(food78$city))
food_data78 <- cbind(food78, county)

food79 <- do.call("rbind", results_list79)
county <- rep("Oscoda", length(food79$city))
food_data79 <- cbind(food79, county)

food80 <- do.call("rbind", results_list80)
county <- rep("Schoolcraft", length(food80$city))
food_data80 <- cbind(food80, county)

food81 <- do.call("rbind", results_list81)
county <- rep("Luce", length(food81$city))
food_data81 <- cbind(food81, county)

food82 <- do.call("rbind", results_list82)
county <- rep("Ontonagon", length(food82$city))
food_data82 <- cbind(food82, county)

food83 <- do.call("rbind", results_list83)
county <- rep("Keweenaw", length(food83$city))
food_data83 <- cbind(food83, county)
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Then, in order to have one dataset that merges all 83 counties of Michigan, we will append as follows, and call our final dataset for cuisines and counties "all_establishments":

```{r}
#append 83 datasets
all_establishments <- rbind(
  food_data, food_data2, food_data3, food_data4, food_data5, food_data6,
  food_data7, food_data8, food_data9, food_data10, food_data11, food_data12,
  food_data13, food_data14, food_data15, food_data16, food_data17, food_data18,
  food_data19, food_data20, food_data21, food_data22, food_data23, food_data24,
  food_data25, food_data26, food_data27, food_data28, food_data29, food_data30,
  food_data31, food_data32, food_data33, food_data34, food_data35, food_data36,
  food_data37, food_data38, food_data39, food_data40, food_data41, food_data42,
  food_data43, food_data44, food_data45, food_data46, food_data47, food_data48,
  food_data49, food_data50, food_data51, food_data52, food_data53, food_data54,
  food_data55, food_data56, food_data57, food_data58, food_data59, food_data60,
  food_data61, food_data62, food_data63, food_data64, food_data65, food_data66,
  food_data67, food_data68, food_data69, food_data70, food_data71, food_data72,
  food_data73, food_data74, food_data75, food_data76, food_data77, food_data78,
  food_data79, food_data80, food_data81, food_data82, food_data83)
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;One of the columns of interest in all_establishments, 'categories', requires some clean-up with formatting. Additionally, we will need to place the categories into new appropriate buckets to make analysis relevant. Thus, we will reformat that column in order to make it more understandable and clear. We show a few examples of classifying 'categories' in the following chunk:

```{r, warning = FALSE}
#clean up 'categories'
all_establishments$categories <- all_establishments$categories %>%
  str_replace_all(., "list\\(alias = ", "") %>%
  str_replace_all(., "\\)", "") %>%
  str_replace_all(., ", title = ", "") %>%
  str_replace_all(., "\"", "") %>%
  str_replace_all(., "burgersBurgers", "American") %>%
  str_replace_all(., "newamericanAmerican \\(New", "American") %>%
  str_replace_all(., "beergardensBeer Gardens", "Bars/Breweries")
```


```{r, include = FALSE}
#clean up the remainder of 'categories'
all_establishments$categories <- all_establishments$categories %>%
  str_replace_all(., "barsBars", "Bars/Breweries") %>%
  str_replace_all(., "bakeriesBakeries", "Cafes/Dessert") %>%
  str_replace_all(., "african", "") %>%
  str_replace_all(., "bubbleteaBubble Tea", "Cafes/Dessert") %>%
  str_replace_all(., "coffeeCoffee & Tea", "Cafes/Dessert") %>%
  str_replace_all(., "tradamericanAmerican \\(Traditional", "American") %>%
  str_replace_all(., "cafesCafes", "Cafes/Dessert") %>%
  str_replace_all(., "breweriesBreweries", "Bars/Breweries") %>%
  str_replace_all(., "hotdogHot Dogs", "American") %>%
  str_replace_all(., "icecreamIce Cream & Frozen Yogurt", "Cafes/Dessert") %>%
  str_replace_all(., "teaTea Rooms", "Cafes/Dessert") %>%
  str_replace_all(., "sportsbarsSports Bars", "Bars/Breweries") %>%
  str_replace_all(., "brewpubsBrewpubs", "Bars/Breweries") %>%
  str_replace_all(., "hotdogsFast Food", "American") %>%
  str_replace_all(., "chocolateChocolatiers & Shops", "Cafes/Dessert") %>%
  str_replace_all(., "candyCandy Stores", "Cafes/Dessert") %>%
  str_replace_all(., "donutsDonuts", "Cafes/Dessert") %>%
  str_replace_all(., "juicebarsJuice Bars & Smoothies", "Cafes/Dessert") %>%
  str_replace_all(., "cocktailbarsCocktail Bars", "Bars/Breweries") %>%
  str_replace_all(., "coffeeroasteriesCoffee Roasteries", "Cafes/Dessert") %>%
  str_replace_all(., "beer_and_wineBeer, Wine & Spirits", "Bars/Breweries") %>%
  str_replace_all(., "bbqBarbeque", "American") %>%
  str_replace_all(., "italian", "") %>%
  str_replace_all(., "wineriesWineries", "Bars/Breweries") %>%
  str_replace_all(., "vietnameseVietnamese", "Southeast Asian") %>%
  str_replace_all(., "burmeseBurmese", "Southeast Asian") %>%
  str_replace_all(., "thaiThai", "Southeast Asian") %>%
  str_replace_all(., "teaTea Rooms", "Cafes/Dessert") %>%
  str_replace_all(., "sushiSushi Bars", "Japanese/Hawaiian") %>%
  str_replace_all(., "pokePoke", "Japanese/Hawaiian") %>%
  str_replace_all(., "ramenRamen", "Japanese/Hawaiian") %>%
  str_replace_all(., "japaneseJapanese", "Japanese/Hawaiian") %>%
  str_replace_all(., "grocery", "") %>%
  str_replace_all(., "greekGreek", "Mediterranean/Middle Eastern") %>%
  str_replace_all(., "fishnchipsFish & Chips", "Misc. European") %>%
  str_replace_all(., "frenchFrench", "Misc. European") %>%
  str_replace_all(., "germanGerman", "Misc. European") %>%
  str_replace_all(., "distilleriesDistilleries", "Bars/Breweries") %>%
  str_replace_all(., "divebarsDive Bars", "Bars/Breweries") %>%
  str_replace_all(., "dessertsDesserts", "Cafes/Dessert") %>%
  str_replace_all(., "delisDelis", "Delis/Sandwiches") %>%
  str_replace_all(., "cupcakesCupcakes", "Cafes/Dessert") %>%
  str_replace_all(., "creperiesCreperies", "Cafes/Dessert") %>%
  str_replace_all(., "mexican", "") %>%
  str_replace_all(., "britishBritish", "Misc. European") %>%
  str_replace_all(., "breakfast_brunch", "") %>%
  str_replace_all(., "chinese", "") %>%
  str_replace_all(., "koreanKorean", "Misc. Asian") %>%
  str_replace_all(., "asianfusionAsian Fusion", "Misc. Asian") %>%
  str_replace_all(., "tex-mexTex-Mex", "Mexican") %>%
  str_replace_all(., "tacosTacos", "Mexican") %>%
  str_replace_all(., "southernSouthern", "American") %>%
  str_replace_all(., "pizzaPizza", "Pizza") %>%
  str_replace_all(., "noodlesNoodles", "Japanese/Hawaiian") %>%
  str_replace_all(., "panasianPan Asian", "Misc. Asian") %>%
  str_replace_all(., "modern_europeanModern European", "Misc. European") %>%
  str_replace_all(., "mideasternMiddle Eastern", "Mediterranean/Middle Eastern") %>%
  str_replace_all(., "sandwichesSandwiches", "Delis/Sandwiches") %>%
  str_replace_all(., "pubsPubs", "Bars/Breweries") %>%
  str_replace_all(., "polishPolish", "Misc. European") %>%
  str_replace_all(., "mediterraneanMediterranean", "Mediterranean/Middle Eastern") %>%
  str_replace_all(., "lebaneseLebanese", "Mediterranean/Middle Eastern") %>%
  str_replace_all(., "steakSteakhouses", "Steakhouses") %>%
  str_replace_all(., "smokehouseSmokehouse", "Steakhouses") %>%
  str_replace_all(., "streetvendorsStreet Vendors", "Misc. Asian") %>%
  str_replace_all(., "saladSalad", "Salad") %>%
  str_replace_all(., "scandinavianScandinavian", "Misc. European") %>%
  str_replace_all(., "seafoodSeafood", "Seafood") %>%
  str_replace_all(., "seafoodmarketsSeafood Markets", "Seafood") %>%
  str_replace_all(., "wrapsWraps", "Delis/Sandwiches") %>%
  str_replace_all(., "venezuelanVenezuelan", "Latin/Spanish") %>%
  str_replace_all(., "veganVegan", "Vegan/Vegetarian") %>%
  str_replace_all(., "vegetarianVegetarian", "Vegan/Vegetarian") %>%
  str_replace_all(., "tapasTapas Bars", "Latin/Spanish") %>%
  str_replace_all(., "tapasmallplatesTapas/Small Plates", "Latin/Spanish") %>%
  str_replace_all(., "popuprestaurantsPop-Up Restaurants", "American") %>%
  str_replace_all(., "latinLatin American", "Latin/Spanish") %>%
  str_replace_all(., "wine_barsWine Bars", "Bars/Breweries") %>%
  str_replace_all(., "bagelsBagels", "Delis/Sandwiches") %>%
  str_replace_all(., "bedbreakfastBed & Breakfast", "Breakfast & Brunch") %>%
  str_replace_all(., "belgianBelgian", "Misc. European") %>%
  str_replace_all(., "beerbarBeer Bar", "Bars/Breweries") %>%
  str_replace_all(., "butcherButcher", "Meat") %>%
  str_replace_all(., "meatsMeat Shops", "Meat") %>%
  str_replace_all(., "buffetsBuffets", "Buffets") %>%
  str_replace_all(., "cajunCajun/Creole", "Cajun/Caribbean") %>%
  str_replace_all(., "caribbeanCaribbean", "Cajun/Caribbean") %>%
  str_replace_all(., "cafeteriaCafeteria", "American") %>%
  str_replace_all(., "chicken_wingsChicken Wings", "Chickens/Wings") %>%
  str_replace_all(., "chickenshopChicken Shop", "Chickens/Wings") %>%
  str_replace_all(., "comfortfoodComfort Food", "American") %>%
  str_replace_all(., "customcakesCustom Cakes", "Cafes/Dessert") %>%
  str_replace_all(., "cubanCuban", "Latin/Spanish") %>%
  str_replace_all(., "dinersDiners", "Diners") %>%
  str_replace_all(., "gluten_freeGluten-Free", "Vegan/Vegetarian") %>%
  str_replace_all(., "vacation_rentalsVacation Rentals", "Non-restaurant") %>%
  str_replace_all(., "venuesVenues & Event Spaces", "Non-restaurant") %>%
  str_replace_all(., "theaterPerforming Arts", "Non-restaurant") %>%
  str_replace_all(., "souvenirsSouvenir Shops", "Non-restaurant") %>%
  str_replace_all(., "servicestationsGas Stations", "Non-restaurant") %>%
  str_replace_all(., "partysuppliesParty Supplies", "Non-restaurant") %>%
  str_replace_all(., "musicvideoMusic & DVDs", "Non-restaurant") %>%
  str_replace_all(., "newcanadianCanadian \\(New", "Bars/Breweries") %>%
  str_replace_all(., "marketsFruits & Veggies", "Fruits & Veggies") %>%
  str_replace_all(., "importedfoodImported Food", "Misc. European") %>%
  str_replace_all(., "hotelsHotels", "Non-restaurant") %>%
  str_replace_all(., "halalHalal", "Mediterranean/Middle Eastern") %>%
  str_replace_all(., "hairHair Salons", "Non-restaurant") %>%
  str_replace_all(., "healthmarketsHealth Markets", "Grocery") %>%
  str_replace_all(., "indonesianIndonesian", "Southeast Asian") %>%
  str_replace_all(., "indpakIndian", "Indian") %>%
  str_replace_all(., "himalayanHimalayan/Nepalese", "Misc. Asian") %>%
  str_replace_all(., "loungesLounges", "Non-restaurant") %>%
  str_replace_all(., "soulfoodSoul Food", "American") %>%
  str_replace_all(., "soupSoup", "American") %>%
  str_replace_all(., "golfGolf", "Non-restaurant") %>%
  str_replace_all(., "giftshopsGift Shops", "Non-restaurant") %>%
  str_replace_all(., "gastropubsGastropubs", "Bars/Breweries") %>%
  str_replace_all(., "foodtrucksFood Trucks", "Mexican") %>%
  str_replace_all(., "foodstandsFood Stands", "American") %>%
  str_replace_all(., "flowersFlowers & Gifts", "Non-restaurant") %>%
  str_replace_all(., "farmersmarketFarmers Market", "Grocery") %>%
  str_replace_all(., "drugstoresDrugstores", "Grocery") %>%
  str_replace_all(., "deptstoresDepartment Stores", "Grocery") %>%
  str_replace_all(., "convenienceConvenience Stores", "Grocery") %>%
  str_replace_all(., "cateringCaterers", "American") %>%
  str_replace_all(., "brazilianBrazilian", "Latin/Spanish") %>%
  str_replace_all(., "bowlingBowling", "Non-restaurant") %>%
  str_replace_all(., "bookstoresBookstores", "Non-restaurant") %>%
  str_replace_all(., "gourmetSpecialty Food", "Other") %>%
  str_replace_all(., "restaurantsRestaurants", "Other") %>%
  str_replace_all(., "arcadesArcades", "Other")
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Our initially cleaned dataset of cuisines and counties (all_establishments) has 1570 observations since the most populated area of certain counties have less than 20 food establishment options on Yelp. However, we have noticed that more data-cleaning may be required. For instance, Yelp has captured establishments that are not helpful with comparing against obesity (i.e. bowling). We have grouped these establishments into a category called "Non-restaurant." Grocery stores ("Grocery" in our dataset) are also more difficult to predict how dietary choices in counties affect obesity since we cannot speculate if a consumer made a healthy or an unhealthy choice at the specific grocery store. Lastly, we had a small group of establishments that did not fit into any categories, so we placed them in a category we called "Other." As these three categories may not be very useful in our analysis, we will remove them from our dataset, shown below.

```{r}
all_establishments <- all_establishments %>% 
  filter(!categories == "Non-restaurant") %>%
  filter(!categories == "Grocery") %>%
  filter(!categories == "Other")
```


```{r, include = FALSE}
all_establishments %>% mutate_if(is.factor, as.character) -> all_establishments
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;After removing the "Non-restaurant", "Grocery", and "Other" categories from all_establishments, our final dataset of cuisines and counties includes 1480 unique observations.

### _Obesity Data_

```{r, warning = FALSE}
obesity <- read_csv("https://raw.githubusercontent.com/daraeoh/survmeth727/master/obesity.csv")
```

```{r}
obesity_avg <- 
  (obesity$female_obesity_prevalence_percent + obesity$male_obesity_prevalence_percent) / 2
avg_obesity <- cbind(obesity, obesity_avg)
```

```{r, include = FALSE}
avg_obesity %>% mutate_if(is.factor, as.character) -> avg_obesity
```

### _Master Data_

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Now that we have gathered both the Cuisines and Counties Data and the Obesity Data, we will merge them together by "county" to get our master spreadsheet for analysis.

```{r, warning = FALSE}
master <-inner_join(all_establishments, avg_obesity, by = "county")
```

## Results

### _Data Exploration_

```{r}
#basic barplot
ggplot(master) + 
  geom_bar(aes(x = categories)) + 
  labs(
    x = "Cuisine Category", 
    y = "Frequency", 
    title = "Frequency of Cuisine Categories on Yelp"
    ) + 
  coord_flip()
```

```{r fig.height = 10, fig.width = 10}
#male obesity barplot by county
male <- aggregate(
  male_obesity_prevalence_percent ~ county, master, mean) %>%
  arrange(desc(male_obesity_prevalence_percent))
male_plot <- ggplot(male, 
                    aes(x = reorder(county, male_obesity_prevalence_percent), 
                        y = male_obesity_prevalence_percent)) + 
  geom_bar(
    stat = "identity", 
    color = 'skyblue', 
    fill = 'steelblue') + 
  labs(
    x = "County", 
    y = "Male Obesity Percent", 
    title = "Male Obesity Percent by County"
    ) +
  coord_flip()

#female obesity barplot by county
female <- aggregate(
  female_obesity_prevalence_percent ~ county, master, mean) %>%
  arrange(desc(female_obesity_prevalence_percent))
female_plot <- ggplot(female, 
                    aes(x = reorder(county, female_obesity_prevalence_percent), 
                        y = female_obesity_prevalence_percent)) + 
  geom_bar(
    stat = "identity", 
    color = 'lightpink', 
    fill = 'pink') + 
  labs(
    x = "", 
    y = "Female Obesity Percent", 
    title = "Female Obesity Percent by County"
    ) +
  coord_flip()

#print male and female obesity barplots
grid.arrange(male_plot, female_plot, ncol = 2)
```

```{r, eval = FALSE}
#top 10 cuisine categories arranged by highest average aggregate rate of obesity
top_categories <- aggregate(
  obesity_avg ~ categories, master, mean) %>%
  arrange(desc(obesity_avg))
head(top_categories, 10)
```

<!-- Table of top 10 cuisine categories arranged by highest average aggregate rate of obesity -->
Cuisine Categories | Average Aggregate Rate of Obesity (%)
------------------ | -------------------------------------
African | 40.45000
Fruits & Veggies	| 39.97500		
Chinese	| 39.30417		
Diners	| 39.23810		
Indian	| 38.99000		
Buffets	| 38.98750		
Pizza	| 38.70844		
Salad	| 38.63462		
Delis/Sandwiches	| 38.51750		
Bars/Breweries	| 38.44529	

```{r, eval = FALSE}
#top 10 counties arranged by highest average aggregate rate of obesity
top_counties <- aggregate(
  obesity_avg ~ county, master, mean) %>%
  arrange(desc(obesity_avg))
head(top_counties, 10)
```

<!-- Table of top 10 counties arranged by highest average aggregate rate of obesity -->
County | Average Aggregate Rate of Obesity (%)
------ | -------------------------------------
Saginaw	| 44.85		
Genesee	| 43.65		
Lake	| 43.25		
Gratiot	| 43.20		
Ionia	| 42.45		
Calhoun	| 42.20		
Arenac	| 42.10		
Monroe	| 41.60		
Oceana	| 41.35		
Wayne	| 41.30

### _Analysis_

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Christoph: This section presents the main results, such as (for example) stats and graphs that show relationships, model results and/or clustering, PCA, etc.

## Discussion

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Christoph: This section summarizes the results and may briefly outline advantages and limitations of the work presented.

## Link to GitHub Repository

https://github.com/daraeoh/survmeth727

## References
